RVD2: An ultra-sensitive variant detection model for low-depth targeted next-generation sequencing data

### 2013-11-26 doc/bioinformatics2013/RVD2.tex
updated gitignore minor manuscript changes.

Figure~\ref{fig:brca_MAF} shows the estimated minor allele frequencies for the normal and tumor samples at the called locations. Positions chr7:743899XC$\rightarrow$T, chr7:753635T$\rightarrow$C and chr7:780960C$\rightarrow$T are germline homozygous mutations. Positions chr7:754371 and chr7:758813 are called heterozygous in the normal sample. In the tumor cells we identified all five mutations chr7:743899C$\rightarrow$T, chr7:753635T$\rightarrow$C, chr7:754371T$\rightarrow$C, chr7:758813G$\rightarrow$A, and chr7:780960C$\rightarrow$T. Positions chr7:754371T$\rightarrow$C and chr7:758813G$\rightarrow$A are identified as loss-of-heterozygosity events.

@@

%%%%%%%%%%%%%%%%%
% Appendix D: Parameter Settings for Variant Calling Algorithms
%%%%%%%%%%%%%%%%%
\section*{Parameter setting for other variant calling algorithms}

>>>>

Figure~\ref{fig:brca_MAF} shows the estimated minor allele frequencies for the normal and tumor samples at the called locations. Positions chr7:743899XC$>$T, chr7:753635T$>$C and chr7:780960C$>$T are germline homozygous mutations. Positions chr7:754371 and chr7:758813 are called heterozygous in the normal sample. In the tumor cells we identified all five mutations chr7:743899C$>$T, chr7:753635T$>$C, chr7:754371T$>$C, chr7:758813G$>$A, and chr7:780960C$>$T. Positions chr7:754371T$>$C and chr7:758813G$>$A are identified as loss-of-heterozygosity events.

@@

%%%%%%%%%%%%%%%%%
% Appendix D: Parameter Settings for Variant Calling Algorithms
%%%%%%%%%%%%%%%%%
\section{Parameter settings for other variant calling algorithms}
